---
title: 'R Assignment #1'
author: "Floriann Deepika, Ellen Mendy, Karan Saeedi"
output:
  pdf_document:
    number_sections: yes
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Include packages here
#Package to read csv from url (https)
#install.packages("readr")
library (readr)
```

# COVID-19 Data Sources
# Data Source : JHU(https://www.jhu.edu/) Data Set by OWID - Our World in Data - https://ourworldindata.org/
# Data Source : Git Hub of OWID : Auto update from JHU
# Worldwide data for each countries - daily auto extracted from JHU(https://github.com/owid/covid-19-data/tree/master/public/data/latest)

```{r data}
# Your script to download and load the data into data frames
urlfile= "https://github.com/owid/covid-19-data/raw/master/public/data/latest/owid-covid-latest.csv"

#read Data Source from url to a data frame
sourceData<-read_csv(url(urlfile))

#write data in local disk for reference
#write.csv(sourceData,"file path")

#Basic EDA
summary(sourceData)
spec(sourceData)
head(sourceData)
```


# Variables

*Your five selected variables and descriptions*
#choosing only the required variables
c19Data <- subset(sourceData, select=c("location","last_updated_date","total_cases","new_cases","new_cases_smoothed","total_deaths","new_deaths","new_deaths_smoothed","total_cases_per_million","new_cases_per_million","new_tests","new_tests_per_thousand","positive_rate","people_fully_vaccinated_per_hundred"))
head(c19Data)
#Varable1 - new_cases
#Variable2 - new_deaths
#Variable3 - new_cases_per_million
#variable4 - positivity rate
#variable5 - people_fully_vaccinated_per_hundred

# First exploration

```{r variable1}
# First exploration
```

```{r variable2}
# First exploration
```

```{r variable3}
# First exploration
```

```{r variable4}
# First exploration
```

```{r variable5}
# First exploration
```

# Questions

*Your three questions*